A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-01-27 manuscript.Rmd
add more realistic simulation function

But wait `lavaan` warns us that this model may not be identified.
We overlooked a crucial assumption of this model, that is measurement invariance.
This assumption is also baked into our simulation of the data.
It is probably more realistic to violate this assumption and plan our analysis accordingly.
Therefore, we simulate the data so that some of the items parameter differ among groups and then alter the analysis to assume partial measurement invariance.
While reconsidering our assumptions, it is also unlikely that the data is normally distributed.
Not only would the actual items be Likert-like and therefore categorical, but also are the in @Jones2013 reported means not in the middle of the scale, thus suggesting some skewness to the items.
@Rhemtulla2012 conclude that using Likert-like items is acceptable when they employ five or more categories.
Hence, we continue simulating continues data.
However, adding a little skewness to the items is easy and helps make the simulation more realistically.
Anyhow, remember that what we consider realistically for our case could be unfit for your case.
<!--Hands-on: build simple functions tailored for your analysis-->

>>>>

But wait `lavaan` warns us that this model may not be identified.
We overlooked a crucial assumption of this model, that is measurement invariance.
This assumption is also baked into our simulation of the data.
It is probably more realistic to violate this assumption and plan our analysis accordingly.
Therefore, we simulate the data so that some of the items parameter differ among groups and then alter the analysis to assume partial measurement invariance.
While reconsidering our assumptions, it is also unlikely that the data is normally distributed.
Not only would the actual items be Likert-like and therefore categorical, but also are the in @Jones2013 reported means not in the middle of the scale, thus suggesting some skewness to the items.
@Rhemtulla2012 conclude that using Likert-like items is acceptable when they employ five or more categories.
Hence, we continue simulating continues data.
However, adding a little skewness to the items is easy and helps make the simulation more realistic.
Anyhow, remember that what we consider realistic for our case could be unfit for your case.
If you are satisfied with your assumptions it helps to write a function that expresses them, like this one:
<!--Hands-on: build simple functions tailored for your analysis-->

```{r generate}
```

Note however that this function is again composed of several functions, which you may inspect on `r link("https://github.com/aaronpeikert/repro-tutorial/blob/master/R/simulation.R", "GitHub")`.

With its help we can simulate 500 cases with a mean difference between groups of 0.1, where the intercepts of three random items vary by .3 and three loadings vary by 30% and five random items have a skew.

```{r}
simulated <- generate(n = 500,
                      diff = 0.1,
                      vary_intercepts = rep(0.3, 3),
                      vary_loadings = rep(0.3, 3),
                      skewness = rep(5, -0.5))
```

```{r}
fit <-
  lavaan::cfa(
    model,
    data = simulated,
    group = "group",
    meanstructure = TRUE,
    std.lv = TRUE,
    group.equal = c("intercepts", "loadings")
  ) 
```
